Deep Reinforcement Learning for Conservation Decisions

### 2021-05-13 manuscript/manuscript.Rmd
Getting into intro agent para

@@

Neural networks become useful in RL when the environment has a large state-action space, which happens frequently with realistic decision-making problems. 
Classic RL algorithms, like policy iteration, value iteration and Actor-Critic [@suttonbarto], fail when the state-action space is large, e.g. when the possible states and actions can not be represented in a tractable table [@CITE].
Yet, over the last 10 years, researchers have shown that neural network-based RL algorithms can perform well on previously unsolvable environments.
Neural networks have been widely useful in reinforcement learning because neural nets have the property of being general function approximators [@CITE].
Whenever there is a need for an agent to approximate some function, say a policy function, value function or a transition function, neural networks can be used in this capacity.
While there are other function approximators that can be used in RL, e.g. Gaussian processes, neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@CITE].
We will not discuss in detail how neural networks work -- see [@CITE] for further background --, but the general process for how neural networks are used in RL is that at each learning step, the agent, say a policy gradient-based agent, will adjust the parameters in its policy neural network so that according to past experiences, the agent will be more likely to engage in highly rewarding behavior in the future. 
This same process occurs in value learning and actor-critic-based deep RL algorithms, except these agents are adjusting either a value network or both a value and policy network respectively.

@@

## Designing and training an agent

The training an agent on an environment involves allowing the agent to experience and respond to repeated simulations from the environment, thousands or even millions of times. 
Over the course of training, weights on the neural network are updated in response to the reward given by the environment, much like reinforcement learning is believed to work in living creatures [@cite].
A neural network can be thought of as a generic function approximator, and these weights as parameters of that function that are estimated from 'data' generated by training.
A typical neural network in RL may have thousands or hundreds of thousands of parameters, giving it the flexibility to learn very complex behaviors.
The overall architecture of the neural network, as well as other parameters such as those governing how an agent learns, how an agent proposes actions, and how the agent discounts future rewards, and so forth are controlled by *hyperparameters*.
To initialize a new, untrained agent, we must specify a handful or so of these hyperparameters, which are held fixed over the course of training.
The particular selection of hyperparameters required depends on which *RL algorithm* our agent will be based.
The RL algorithm specifies precisely how the agent will learn from its environment:
Is the algorithm model-based or model-free? 
Stochastic or deterministic? 
"Off-policy" or "on-policy"? 
Does it use a random noise model to propose actions?
Does it permit a continuous action space or require discrete actions?
The design of RL algorithms has been and remains an area of intense research and rapid development [Table 2].
Open source implementations by professional software development teams often follow swiftly after new algorithms are published [@Ssb3; @tf-agents].
In the following section, we summarize some of the key concepts that make up an RL algorithm, and highlight relevant distinctions between important algorithms today.

>>>>

<!-- Write paragraph on classic approaches then compare to deep RL very broadly-->

@@

Neural networks become useful in RL when the environment has a large state-action space, which happens frequently with realistic decision-making problems. 
Classic RL algorithms, like policy iteration, value iteration and TD-learning [@suttonbarto], fail when the state-action space is large, e.g. when the possible states and actions can not be represented in a tractable table [@CITE].
Yet, over the last 10 years, researchers have shown that neural network-based RL algorithms can perform well on previously unsolvable environments.
Neural networks have been widely useful in reinforcement learning because neural nets have the property of being general function approximators [@CITE].
Whenever there is a need for an agent to approximate some function, say a policy function, value function or a transition function, neural networks can be used in this capacity.
While there are other function approximators that can be used in RL, e.g. Gaussian processes, neural networks have excelled in this role because of their ability to learn complex, non-linear, high dimensional functions and their ability to adapt given new information [@CITE].
We will not discuss in detail how neural networks work -- see [@CITE] for further background --, but the general process for how neural networks are used in RL is that at each learning step, the agent, say a policy gradient-based agent, will adjust the parameters in its policy neural network so that according to past experiences, the agent will be more likely to engage in highly rewarding behavior in the future. 
This same process occurs in value learning and actor-critic-based deep RL algorithms, except these agents are adjusting either a value network or both a value and policy network respectively.

@@

## Designing and training an agent
<!-- Maybe rename this as Training and Tuning an Agent -> how to practically get an agent up and running -->

Training a deep, model-free agent on an environment involves allowing the agent to interact with the environment for thousands or even millions of time steps. 
Over the course of training, the agent will engage in a trial and error process whereby the agent continually updates weights on a collection of neural networks in response to the environment's reward signal, much like how reinforcement learning is believed to work in living creatures [@cite].
Fundamental to this trial and error process is a balancing of explorative and exploitative behavior.
The agent will occasionally need to propose exploratory actions that may result in higher rewards than previously seen. 
Yet, the agent will also need to occasionally exploit the best perceived sequence of actions which may require marginal improvement to reach optimality.
As the exploration-exploitation is currently unsolved, there are a range of approaches that RL algorithms employ.

Model-free algorithms can explore the environment in either an off-policy or on-policy manner. 
The distinction here comes from what policy the agent is using during training.
For off-policy algorithms, the agent is using a policy that can be different than the policy the agent will use during evaluation to select actions; while in on-policy algoirthms, the agent uses the same policy in training as the agent will use during evaluation.
On top of this distinction, agents can learn either a deterministic or stochastic policy.

A neural network can be thought of as a generic function approximator, and these weights as parameters of that function that are estimated from 'data' generated by training.
A typical neural network in RL may have thousands or hundreds of thousands of parameters, giving it the flexibility to learn very complex behaviors.
The overall architecture of the neural network, as well as other parameters such as those governing how an agent learns, how an agent proposes actions, and how the agent discounts future rewards, and so forth are controlled by *hyperparameters*.
To initialize a new, untrained agent, we must specify a handful or so of these hyperparameters, which are held fixed over the course of training.
The particular selection of hyperparameters required depends on which *RL algorithm* our agent will be based.
The RL algorithm specifies precisely how the agent will learn from its environment:
Is the algorithm model-based or model-free? 
Stochastic or deterministic? 
"Off-policy" or "on-policy"? 
Does it use a random noise model to propose actions?
Does it permit a continuous action space or require discrete actions?
The design of RL algorithms has been and remains an area of intense research and rapid development [Table 2].
Open source implementations by professional software development teams often follow swiftly after new algorithms are published [@Ssb3; @tf-agents].
In the following section, we summarize some of the key concepts that make up an RL algorithm, and highlight relevant distinctions between important algorithms today.
